Introducing statistics with \texttt{intRo}

### 2014-11-10 student-paper-competition-2014/paper.Rmd
Some more text for the education section

The features of \texttt{intRo} were selected in order to apply to the most commonly used lesson plans in early statistics courses. The textbook "The Art and Science of Learning from Data" by Agresti and Franklin references many of the focal points of introductory statistics, and \texttt{intRo} supports performing a majority of them. Part one, titled "Gathering and Exploring Data", covers graphical summaries, measures of spread and center, and avoiding the misuse of graphics in situations they are not appropriate. \texttt{intRo} includes modules for both graphical and numerical summaries covering these topics. Furthermore, \texttt{intRo} limits the display of variables to ones that are appropriate for a chosen plot type, helping to reinforce the appropriateness of particular graphics.

@@

>>>>

The features of \texttt{intRo} were selected in order to apply to the most commonly used lesson plans in early statistics courses. The textbook "The Art and Science of Learning from Data" by Agresti and Franklin references many of the focal points of introductory statistics, and \texttt{intRo} supports performing a majority of them. Part one, titled "Gathering and Exploring Data", covers graphical summaries, measures of spread and center, and avoiding the misuse of graphics in situations they are not appropriate. \texttt{intRo} includes modules for both graphical and numerical summaries covering these topics. Furthermore, \texttt{intRo} limits the display of variables to ones that are appropriate for a chosen plot type, helping to reinforce the appropriateness of particular graphics (Figure \ref{fig:ag}).

@@

Part two of this text discusses probability and sampling distributions, which is outside the current realm of \texttt{intRo}, but part three focuses on inferential statistics. The inferential statistics include confidence intervals, hypothesis testing, and comparing two variables, all supported natively in \texttt{intRo}. Finally, part four of the text discusses the association between variables, including regression, functions that intRo performs with ease. Some of the more advanced topics of this section are currently unsupported by \texttt{intRo}, including multiple regression and nonparametric statistics.

Statistics courses with a lab component can most benefit from the use of \texttt{intRo}. As students learn the aforementioned concepts, they can practice using the tools to perform the statistical tests and summaries. They simply upload a dataset and click the module appropriate to the section of the class. Once they choose the options desired by the instructor (variables, confidence levels, etc.), they can view the results and ultimately print the output for turning in. Early labs can walk the user through the limited number of button presses and clicks necessary, while later labs can more vaguely describe the intended output in hopes that the user can easily navigate the \texttt{intRo} interface to obtain the results. For topics currently unsupported by \texttt{intRo}, the instructor can supplement the its use with other web-based modules that are publicly available.
